Viscous Transport in Eroding Porous Media

### 2019-08-25 docs/transport/erosion_transport.tex
working on results

\todo[inline]{Bryan is here}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{20 Bodies at a Medium Porosity}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
We consider 20 eroding bodies that are discretized with $N_\iin=256$
points and are initially placed in $[-1,1] \times [-1,1]$.  The
background flow is the Hagen-Poiseuille flow
\begin{align}
  \UU(\xx)=U \left[
  \begin{array}{c}
    1-y^2 \\ 0
  \end{array}
  \right],
\end{align}
where the flow rate $U$ is chosen so that the pressure drop from $x=-2$
to $x=2$ is held fixed at 2.  We start by analyzing the effect of
erosion on the area fraction and the flow rate.  In
Figure~\ref{fig:Eroding20flowrate}(a), we plot the area fraction as a
function of normalized time.  Initially, 62\% of the geometry is eroded
bodies corresponding to a porosity of $0.38$, and the area fraction
decreases to 0 as the bodies erode.  The trend of the area fraction
resembles that of our previous work~\cite{qua-moo2018} (Figure 10(a)),
but with a larger initial area fraction.  We also compute the flow rate
$U$ required to maintain a constant pressure drop across the channel in
Figure~\ref{fig:Eroding20flowrate}(b).  Again, the trend of $U$
resembles that of our previous work~\cite{qua-moo2018} (Figure 10(b)),
except that the initial flow rate is an order of magnitude smaller
because of the larger initial area fraction.  Starting around normalized
time $0.2$, Figure~\ref{fig:Eroding20flowrate}(b) is roughly linear
which indicates that the flow rate can be written as a power law.  Using
a line of best fit, the flow rate is approximately 
\begin{align} 
  U \approx \left(\frac{t}{t_f}\right)^{3.43},
\end{align}
which is the dashed line in Figure~\ref{fig:Eroding20flowrate}(b).

\begin{figure}[H]
\begin{subfigure}[b]{0.55\textwidth}
\includegraphics*[width =\linewidth]{./figs/porosity20dense}
\caption{}
\end{subfigure}
\begin{subfigure}[b]{0.5\textwidth}
\includegraphics*[width =\linewidth]{./figs/flow_rate20dense}
\caption{}
\end{subfigure}
\caption{\label{fig:Eroding20flowrate}(a): The area fraction of 20
nearly touching eroding bodies versus normalized time. (b): The incoming
flow rate, $U$, for a fixed pressure drop across the channel versus
normalized time.  The flow rate is initially very small, but it
eventually increases as a power law (dashed line) towards the flow rate
$U=1$ that occurs once all the bodies have eroded.}
\end{figure}

Snapshots of the bodies at four equispaced times are shown in
Figure~\ref{fig:Eroding20vort}.  The color is the vorticity which is
equivalent to the shear stress when restricted to the eroding bodies.
Therefore, erosion is fastest in regions where the magnitude of the
vorticity is largest.  Initially, several of the eroding bodies are
closer to the outer wall than the $5h$ threshold required to guarantee
sufficiently accurate quadrature with the trapezoid rule.  In
particular, with $h=L_2/N_\out$, the distance between bodies 1, 6, 13,
and 15 are $1.3h$, $2.9h$, $2.8h$, and $1.3h$, respectively.  In
addition, the distance between several pairs of eroding bodies is too
small to be accurately resolved with the trapezoid rule at the
prescribed resolution.  Particular pairs include bodies 1 \& 6, 3 \& 9,
6 \& 8, and 14 \& 18.  By using the Barycentric quadrature rule, the
interaction between these nearly-touching bodies can be accurately
resolved at the prescribed resolution.

\begin{figure}[H]
\begin{center}
  \includegraphics[height=0.225\textwidth]{./figs/20b_dense1}
  \includegraphics[height=0.225\textwidth]{./figs/20b_dense101}
  \includegraphics[height=0.225\textwidth]{./figs/20b_dense201}
  \includegraphics[height=0.225\textwidth]{./figs/20b_dense301}
\caption{\label{fig:Eroding20vort} Erosion of 20 nearly touching bodies
with the fixed pressure drop condition. The color is the vorticity of
the fluid. The four snapshots are evenly spaced in time. We use $N_\iin
= 256$ discretization points on the bodies and $\Dt=10^{-4}$.  In the
forth frame, bodies 4, 12, and 17 have vanished completely, and body 19
has almost completely eroded.}
\end{center}
\end{figure}

>>>>

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{20 Bodies at a Medium Porosity}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
We consider 20 eroding bodies that are discretized with $N_\iin=256$
points and a time step size of $\Delta t = 10^{-4}$.  The background
flow is the Hagen-Poiseuille flow
\begin{align}
  \UU(\xx)=U \left[
  \begin{array}{c}
    1-y^2 \\ 0
  \end{array}
  \right],
\end{align}
where the flow rate $U$ is chosen so that the pressure drop from $x=-2$
to $x=2$ is held fixed at 2.  We start by analyzing the effect of
erosion on the area fraction and the flow rate.  In
Figure~\ref{fig:Eroding20flowrate}(a), we plot the area fraction as a
function of normalized time.  Initially, 62\% of the geometry is eroded
bodies corresponding to a porosity of $0.38$, and the area fraction
decreases to 0 as the bodies erode.  The trend of the area fraction
resembles that of our previous work~\cite{qua-moo2018} (Figure 10(a)),
but with a larger initial area fraction.  In
Figure~\ref{fig:Eroding20flowrate}(b), we plot flow rate $U$ required to
maintain a constant pressure drop across the channel.  Again, the trend
of $U$ resembles that of our previous work~\cite{qua-moo2018} (Figure
10(b)), except that the initial flow rate is an order of magnitude
smaller because of the larger initial area fraction.  Starting around
normalized time $0.2$, Figure~\ref{fig:Eroding20flowrate}(b) is roughly
linear which indicates that the flow rate can be written as a power law.
Using a line of best fit, the flow rate is approximately 
\begin{align} 
  U \approx \left(\frac{t}{t_f}\right)^{3.43},
\end{align}
which is the dashed line in Figure~\ref{fig:Eroding20flowrate}(b).

\begin{figure}[H]
\begin{subfigure}[b]{0.55\textwidth}
\includegraphics*[width =\linewidth]{./figs/porosity20dense}
\caption{}
\end{subfigure}
\begin{subfigure}[b]{0.5\textwidth}
\includegraphics*[width =\linewidth]{./figs/flow_rate20dense}
\caption{}
\end{subfigure}
\caption{\label{fig:Eroding20flowrate}(a): The area fraction of 20
nearly touching eroding bodies versus normalized time. (b): The flow
rate, $U$, for a fixed pressure drop across the channel versus
normalized time.  The flow rate is initially very small, but it
eventually increases as a power law (dashed line) towards the flow rate
$U=1$ that occurs once all the bodies have eroded.}
\end{figure}

Snapshots of the bodies at four equispaced times are shown in
Figure~\ref{fig:Eroding20vort}.  The color is the vorticity which is
equivalent to the shear stress when restricted to the eroding bodies.
Therefore, erosion is fastest in regions where the magnitude of the
vorticity is largest.  Initially, several of the eroding bodies are
closer to the outer wall than the $5h$ threshold required to guarantee a
machine precision quadrature error for the trapezoid rule.  In
particular, with $h=L_2/N_\out$, the distance between bodies 1, 6, 13,
and 15 and the outer wall are $1.3h$, $2.9h$, $2.8h$, and $1.3h$,
respectively.  In addition, the distance between several pairs of
eroding bodies is too small to be accurately resolved with the trapezoid
rule at the prescribed resolution.  Particular pairs include bodies 1 \&
6, 3 \& 9, 6 \& 8, and 14 \& 18.  By using the Barycentric quadrature
rule, the interaction between these nearly-touching bodies can be
accurately resolved at the prescribed resolution.

\begin{figure}[H]
\begin{center}
  \includegraphics[height=0.225\textwidth]{./figs/20b_dense1}
  \includegraphics[height=0.225\textwidth]{./figs/20b_dense101}
  \includegraphics[height=0.225\textwidth]{./figs/20b_dense201}
  \includegraphics[height=0.225\textwidth]{./figs/20b_dense301}
\caption{\label{fig:Eroding20vort} Erosion of 20 nearly touching bodies
with the fixed pressure drop condition. The color is the vorticity of
the fluid. The four snapshots are evenly spaced in time. We use $N_\iin
= 256$ discretization points on the bodies.  In the fourth frame, bodies
4, 12, and 17 have vanished completely, and body 19 has almost
completely eroded.}
\end{center}
\end{figure}
